Do we need detailed demographic data to forecast plant population responses to climate change?

### 2017-02-27 manuscript/manuscript.tex
just changes font color

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={},
            colorlinks=true,
            citecolor=blue,
            urlcolor=black,
            linkcolor=black,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}

@@

\maketitle

@@

\textbf{Corresponding author:}\\Andrew Tredennick
(\href{mailto:atredenn@gmail.com}{\nolinkurl{atredenn@gmail.com}})\\Department
of Wildland Resources and the Ecology Center\\5230 Old Main Hill\\Utah
State University\\Logan, Utah 84322, USA

@@

Perhaps the greatest challenge for ecology in the 21st century is to
forecast the impacts of environmental change (Clark et al. 2001, Petchey
et al. 2015). Forecasts require sophisticated modeling approaches that
fully account for uncertainty and variability in both ecological process
and model parameters (Luo et al. 2011, but see Perretti et al. 2013).
The increasing statistical sophistication of population models (Rees and
Ellner 2009) makes them promising tools for predicting the impacts of
environmental change on species persistence and abundance. But
reconciling the scales at which population models are parameterized with
the scales at which environmental changes play out remains a challenge
(Clark et al. 2010, 2012, Freckleton et al. 2011, Queenborough et al.
2011). Most population models are built using demographic data from a
single study site because tracking the fates of individuals is so
difficult. The resulting models cannot be applied to the landscape and
regional scales relevant to decision-making without information about
how the estimated parameters respond to spatial variation in biotic and
abiotic drivers (S{æ}ther et al. 2007). The limited spatial extent of
individual-level demographic datasets constrains our ability to use
population models to address applied questions about the consequences of
climate change.

Aggregate measures of population status, rather than individual
performance, offer an intriguing alternative for modeling populations
(Clark and Bj{ø}rnstad 2004, Freckleton et al. 2011). Population-level
data cannot provide inference about demographic mechanisms, but might be
sufficient for modeling future population states, especially because
population-level data, such as plant percent cover, are feasible to
collect across broad spatial extents (e.g., Queenborough et al. 2011).
The choice between individual and population-level data involves a
difficult trade-off: while individual-level data are necessary for
mechanistic models, population-level data enable models that can be
applied over greater spatial and temporal extents. An open question is
how much forecasting skill is lost when we build models based on
population rather than individual-level data.

@@

Adler, P. B., H. J. Dalgleish, and S. P. Ellner. 2012. Forecasting plant
community impacts of climate variability and change: when do competitive
interactions matter? Journal of Ecology 100:478--487.

Adler, P. B., S. P. Ellner, and J. M. Levine. 2010. Coexistence of
perennial plants: An embarrassment of niches. Ecology Letters
13:1019--1029.

Anderson, J., L. Vermeire, and P. B. Adler. 2011. Fourteen years of
mapped, permanent quadrats in a northern mixed prairie, USA. Ecology
92:1703.

Chu, C., and P. B. Adler. 2015. Large niche differences emerge at the
recruitment stage to stabilize grassland coexistence. Ecological
Monographs 85:373--392.

Chu, C., K. M. Havstad, N. Kaplan, W. K. Lauenroth, M. P. McClaran, D.
P. Peters, L. T. Vermeire, and P. B. Adler. 2014. Life form influences
survivorship patterns for 109 herbaceous perennials from six semi-arid
ecosystems. Journal of Vegetation Science 25:947--954.

Chu, C., A. R. Kleinhesselink, K. M. Havstad, M. P. McClaran, D. P.
Peters, L. T. Vermeire, H. Wei, and P. B. Adler. 2016. Direct effects
dominate responses to climate perturbations in grassland plant
communities. Nature Communications 7.

Clark, J. S., and O. N. Bj{ø}rnstad. 2004. Population time series:
Process variability, observation errors, missing values, lags, and
hidden states. Ecology 85:3140--3150.

Clark, J. S., D. M. Bell, M. H. Hersh, M. C. Kwit, E. Moran, C. Salk, A.
Stine, D. Valle, and K. Zhu. 2011. Individual-scale variation,
species-scale differences: Inference needed to understand diversity.
Ecology Letters 14:1273--1287.

Clark, J. S., D. M. Bell, M. Kwit, A. Stine, B. Vierra, and K. Zhu.
2012. Individual-scale inference to anticipate climate-change
vulnerability of biodiversity. Philosophical Transactions of the Royal
Society B: Biological Sciences 367:236--246.

Clark, J. S., D. Bell, C. Chu, B. Courbaud, M. Dietze, M. Hersh, J.
HilleRisLambers, I. Ib{á}{ñ}ez, S. LaDeau, S. McMahon, J. Metcalf, J.
Mohan, E. Moran, L. Pangle, S. Pearson, C. Salk, Z. Shen, D. Valle, and
P. Wyckoff. 2010. High-dimensional coexistence based on individual
variation: a synthesis of evidence. Ecological Monographs 80:569--608.

Clark, J. S., S. R. Carpenter, M. Barber, S. Collins, A. Dobson, J. A.
Foley, D. M. Lodge, M. Pascual, R. Pielke, W. Pizer, C. Pringle, W. V.
Reid, K. A. Rose, O. Sala, W. H. Schlesinger, D. H. Wall, and D. Wear.
2001. Ecological forecasts: an emerging imperative. Science (New York,
N.Y.) 293:657--660.

Cribari-Neto, F. 2004. Asymptotic inference under heteroskedasticity of
unknown form. Computational Statistics and Data Analysis 45:215--233.

Dalgleish, H. J., D. N. Koons, M. B. Hooten, C. A. Moffet, and P. B.
Adler. 2011. Climate influences the demography of three dominant
sagebrush steppe plants. Ecology 92:75--85.

Ellner, S. P., and M. Rees. 2006. Integral projection models for species
with complex demography. The American naturalist 167:410--428.

Evans, M. R. 2012. Modelling ecological systems in a changing world.
Philosophical transactions of the Royal Society of London. Series B,
Biological sciences 367:181--190.

Freckleton, R. P., W. J. Sutherland, A. R. Watkinson, and S. A.
Queenborough. 2011. Density-structured models for plant population
dynamics. American Naturalist 177:1--17.

Gelman, A., J. Hwang, and A. Vehtari. 2014. Understanding predictive
information criteria for Bayesian models. Statistics and Computing
24:997--1016.

Gerber, B. D., W. L. Kendall, M. B. Hooten, J. A. Dubovsky, and R. C.
Drewien. 2015. Optimal population prediction of sandhill crane
recruitment based on climate-mediated habitat limitations. Journal of
Animal Ecology 84:1299--1310.

Hobbs, N. T., and M. B. Hooten. 2015. Bayesian Models: A Statistical
Primer for Ecologists. Princeton University Press, Princeton.

Hooten, M. B., and N. T. Hobbs. 2015. A guide to Bayesian model
selection for ecologists. Ecological Monographs 85:3--28.

Lauenroth, W. K., and P. B. Adler. 2008. Demography of perennial
grassland plants: Survival, life expectancy and life span. Journal of
Ecology 96:1023--1032.

Luo, Y., K. Ogle, C. Tucker, S. Fei, C. Gao, S. LaDeau, J. S. Clark, and
D. S. Schimel. 2011. Ecological forecasting and data assimilation in a
data-rich era. Ecological Applications 21:1429--1442.

Mieszkowska, N., G. Milligan, M. T. Burrows, R. Freckleton, and M.
Spencer. 2013. Dynamic species distribution models from categorical
survey data. Journal of Animal Ecology 82:1215--1226.

Mouquet, N., Y. Lagadeuc, V. Devictor, L. Doyen, A. Duputi{é}, D.
Eveillard, D. Faure, E. Garnier, O. Gimenez, P. Huneman, F. Jabot, P.
Jarne, D. Joly, R. Julliard, S. K{é}fi, G. J. Kergoat, S. Lavorel, L.
{Le Gall}, L. Meslin, S. Morand, X. Morin, H. Morlon, G. Pinay, R.
Pradel, F. M. Schurr, W. Thuiller, and M. Loreau. 2015. Predictive
ecology in a changing world.

Perretti, C. T., S. B. Munch, and G. Sugihara. 2013. Model-free
forecasting outperforms the correct mechanistic model for simulated and
experimental data. Proceedings of the National Academy of Sciences of
the United States of America 110:5253--5257.

Petchey, O. L., M. Pontarp, T. M. Massie, S. K{é}fi, A. Ozgul, M.
Weilenmann, G. M. Palamara, F. Altermatt, B. Matthews, J. M. Levine, D.
Z. Childs, B. J. McGill, M. E. Schaepman, B. Schmid, P. Spaak, A. P.
Beckerman, F. Pennekamp, and I. S. Pearse. 2015. The ecological forecast
horizon, and examples of its uses and determinants. Ecology Letters
18:597--611.

Pol, M. van de, and A. Cockburn. 2011. Identifying the critical climatic
time window that affects trait expression. The American naturalist
177:698--707.

Queenborough, S. A., K. M. Burnet, W. J. Sutherland, A. R. Watkinson,
and R. P. Freckleton. 2011. From meso- to macroscale population
dynamics: A new density-structured approach. Methods in Ecology and
Evolution 2:289--302.

R Core Team. 2013. R: A language and environment for statistical
computing.

Rees, M., and S. P. Ellner. 2009. Integral projection models for
populations in temporally varying environments. Ecological Monographs
79:575--594.

Schindler, D. E., and R. Hilborn. 2015. Prediction, precaution, and
policy under global change. Science 347:953--954.

Sims, M., D. A. Elston, A. Larkham, D. H. Nussey, and S. D. Albon. 2007.
Identifying when weather influences life-history traits of grazing
herbivores. Journal of Animal Ecology 76:761--770.

Stan Development Team. 2014a. Stan: A C++ Library for Probability and
Sampling, Version 2.5.0.

Stan Development Team. 2014b. Rstan: the R interface to Stan, Version
2.5.0.

S{æ}ther, B. E., S. Engen, V. Gr{ø}tan, W. Fiedler, E. Matthysen, M. E.
Visser, J. Wright, A. P. M{ø}ller, F. Adriaensen, H. {Van Balen}, D.
Balmer, M. C. Mainwaring, R. H. McCleery, M. Pampus, and W. Winkel.
2007. The extended Moran effect and large-scale synchronous fluctuations
in the size of great tit and blue tit populations. Journal of Animal
Ecology 76:315--325.

Taylor, C. M., and A. Hastings. 2004. Finding optimal control strategies
for invasive species: a density-structured model for Spartina
alterniflora. Journal of Applied Ecology 41:1049--1057.

Teller, B. J., P. B. Adler, C. B. Edwards, G. Hooker, R. E. Snyder, and
S. P. Ellner. 2016. Linking demography with drivers: climate and
competition. Methods in Ecology and Evolution 7:171--183.

Vehtari, A., A. Gelman, and J. Gabry. 2016. Efficient implementation of
leave-one-out cross-validation and WAIC for evaluating fitted Bayesian
models. ArXiv preprint.

Wilcox, R. R. 2009. Comparing Pearson Correlations: Dealing with
Heteroscedasticity and Nonnormality. Communications in Statistics -
Simulation and Computation 38:2220--2234.

Ye, H., R. J. Beamish, S. M. Glaser, S. C. H. Grant, C.-h. Hsieh, L. J.
Richards, J. T. Schnute, and G. Sugihara. 2015. Equation-free
mechanistic ecosystem forecasting using empirical dynamic modeling.
Proceedings of the National Academy of Sciences 112:E1569--E1576.

>>>>

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
\hypersetup{unicode=true,
            colorlinks=true,
            linkcolor=black,
            citecolor=Blue,
            urlcolor=black,
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\definecolor{blue}{rgb}{0,0,0}

@@

\textbf{Corresponding author:}\\
Andrew Tredennick
(\href{mailto:atredenn@gmail.com}{\nolinkurl{atredenn@gmail.com}})\\
Department of Wildland Resources and the Ecology Center\\
5230 Old Main Hill\\
Utah State University\\
Logan, Utah 84322, USA

@@

Perhaps the greatest challenge for ecology in the 21st century is to
forecast the impacts of environmental change (Clark et al. 2001, Petchey
et al. 2015). Forecasts require sophisticated modeling approaches that
fully account for uncertainty and variability in both ecological process
and model parameters (Luo et al. 2011, but see Perretti et al. 2013).
The increasing statistical sophistication of population models (Rees and
Ellner 2009) makes them promising tools for predicting the impacts of
environmental change on species persistence and abundance. But
reconciling the scales at which population models are parameterized with
the scales at which environmental changes play out remains a challenge
(Clark et al. 2010, 2012, Freckleton et al. 2011, Queenborough et al.
2011). Most population models are built using demographic data from a
single study site because tracking the fates of individuals is so
difficult. The resulting models cannot be applied to the landscape and
regional scales relevant to decision-making without information about
how the estimated parameters respond to spatial variation in biotic and
abiotic drivers (Sæther et al. 2007). The limited spatial extent of
individual-level demographic datasets constrains our ability to use
population models to address applied questions about the consequences of
climate change.

Aggregate measures of population status, rather than individual
performance, offer an intriguing alternative for modeling populations
(Clark and Bjørnstad 2004, Freckleton et al. 2011). Population-level
data cannot provide inference about demographic mechanisms, but might be
sufficient for modeling future population states, especially because
population-level data, such as plant percent cover, are feasible to
collect across broad spatial extents (e.g., Queenborough et al. 2011).
The choice between individual and population-level data involves a
difficult trade-off: while individual-level data are necessary for
mechanistic models, population-level data enable models that can be
applied over greater spatial and temporal extents. An open question is
how much forecasting skill is lost when we build models based on
population rather than individual-level data.

@@

\hypertarget{refs}{}
\hypertarget{ref-Adler2012}{}
Adler, P. B., H. J. Dalgleish, and S. P. Ellner. 2012. Forecasting plant
community impacts of climate variability and change: when do competitive
interactions matter? Journal of Ecology 100:478--487.

\hypertarget{ref-Adler2010}{}
Adler, P. B., S. P. Ellner, and J. M. Levine. 2010. Coexistence of
perennial plants: An embarrassment of niches. Ecology Letters
13:1019--1029.

\hypertarget{ref-Anderson2011}{}
Anderson, J., L. Vermeire, and P. B. Adler. 2011. Fourteen years of
mapped, permanent quadrats in a northern mixed prairie, USA. Ecology
92:1703.

\hypertarget{ref-Chu2015}{}
Chu, C., and P. B. Adler. 2015. Large niche differences emerge at the
recruitment stage to stabilize grassland coexistence. Ecological
Monographs 85:373--392.

\hypertarget{ref-Chu2014a}{}
Chu, C., K. M. Havstad, N. Kaplan, W. K. Lauenroth, M. P. McClaran, D.
P. Peters, L. T. Vermeire, and P. B. Adler. 2014. Life form influences
survivorship patterns for 109 herbaceous perennials from six semi-arid
ecosystems. Journal of Vegetation Science 25:947--954.

\hypertarget{ref-Chu2016}{}
Chu, C., A. R. Kleinhesselink, K. M. Havstad, M. P. McClaran, D. P.
Peters, L. T. Vermeire, H. Wei, and P. B. Adler. 2016. Direct effects
dominate responses to climate perturbations in grassland plant
communities. Nature Communications 7.

\hypertarget{ref-Clark2004}{}
Clark, J. S., and O. N. Bjørnstad. 2004. Population time series: Process
variability, observation errors, missing values, lags, and hidden
states. Ecology 85:3140--3150.

\hypertarget{ref-Clark2011b}{}
Clark, J. S., D. M. Bell, M. H. Hersh, M. C. Kwit, E. Moran, C. Salk, A.
Stine, D. Valle, and K. Zhu. 2011. Individual-scale variation,
species-scale differences: Inference needed to understand diversity.
Ecology Letters 14:1273--1287.

\hypertarget{ref-Clark2012}{}
Clark, J. S., D. M. Bell, M. Kwit, A. Stine, B. Vierra, and K. Zhu.
2012. Individual-scale inference to anticipate climate-change
vulnerability of biodiversity. Philosophical Transactions of the Royal
Society B: Biological Sciences 367:236--246.

\hypertarget{ref-Clark2010}{}
Clark, J. S., D. Bell, C. Chu, B. Courbaud, M. Dietze, M. Hersh, J.
HilleRisLambers, I. Ibáñez, S. LaDeau, S. McMahon, J. Metcalf, J. Mohan,
E. Moran, L. Pangle, S. Pearson, C. Salk, Z. Shen, D. Valle, and P.
Wyckoff. 2010. High-dimensional coexistence based on individual
variation: a synthesis of evidence. Ecological Monographs 80:569--608.

\hypertarget{ref-Clark2001}{}
Clark, J. S., S. R. Carpenter, M. Barber, S. Collins, A. Dobson, J. A.
Foley, D. M. Lodge, M. Pascual, R. Pielke, W. Pizer, C. Pringle, W. V.
Reid, K. A. Rose, O. Sala, W. H. Schlesinger, D. H. Wall, and D. Wear.
2001. Ecological forecasts: an emerging imperative. Science
293:657--660.

\hypertarget{ref-Cribari-Neto2004}{}
Cribari-Neto, F. 2004. Asymptotic inference under heteroskedasticity of
unknown form. Computational Statistics and Data Analysis 45:215--233.

\hypertarget{ref-Dalgleish2011}{}
Dalgleish, H. J., D. N. Koons, M. B. Hooten, C. A. Moffet, and P. B.
Adler. 2011. Climate influences the demography of three dominant
sagebrush steppe plants. Ecology 92:75--85.

\hypertarget{ref-Ellner2006}{}
Ellner, S. P., and M. Rees. 2006. Integral projection models for species
with complex demography. The American naturalist 167:410--428.

\hypertarget{ref-Evans2012b}{}
Evans, M. R. 2012. Modelling ecological systems in a changing world.
Philosophical transactions of the Royal Society of London. Series B,
Biological sciences 367:181--190.

\hypertarget{ref-Freckleton2011}{}
Freckleton, R. P., W. J. Sutherland, A. R. Watkinson, and S. A.
Queenborough. 2011. Density-structured models for plant population
dynamics. American Naturalist 177:1--17.

\hypertarget{ref-Gelman2014}{}
Gelman, A., J. Hwang, and A. Vehtari. 2014. Understanding predictive
information criteria for Bayesian models. Statistics and Computing
24:997--1016.

\hypertarget{ref-Gerber2015}{}
Gerber, B. D., W. L. Kendall, M. B. Hooten, J. A. Dubovsky, and R. C.
Drewien. 2015. Optimal population prediction of sandhill crane
recruitment based on climate-mediated habitat limitations. Journal of
Animal Ecology 84:1299--1310.

\hypertarget{ref-Hobbs2015}{}
Hobbs, N. T., and M. B. Hooten. 2015. Bayesian Models: A Statistical
Primer for Ecologists. Princeton University Press, Princeton.

\hypertarget{ref-Hooten2015}{}
Hooten, M. B., and N. T. Hobbs. 2015. A guide to Bayesian model
selection for ecologists. Ecological Monographs 85:3--28.

\hypertarget{ref-Lauenroth2008}{}
Lauenroth, W. K., and P. B. Adler. 2008. Demography of perennial
grassland plants: Survival, life expectancy and life span. Journal of
Ecology 96:1023--1032.

\hypertarget{ref-Luo2011a}{}
Luo, Y., K. Ogle, C. Tucker, S. Fei, C. Gao, S. LaDeau, J. S. Clark, and
D. S. Schimel. 2011. Ecological forecasting and data assimilation in a
data-rich era. Ecological Applications 21:1429--1442.

\hypertarget{ref-Mieszkowska2013}{}
Mieszkowska, N., G. Milligan, M. T. Burrows, R. Freckleton, and M.
Spencer. 2013. Dynamic species distribution models from categorical
survey data. Journal of Animal Ecology 82:1215--1226.

\hypertarget{ref-Mouquet2015}{}
Mouquet, N., Y. Lagadeuc, V. Devictor, L. Doyen, A. Duputié, D.
Eveillard, D. Faure, E. Garnier, O. Gimenez, P. Huneman, F. Jabot, P.
Jarne, D. Joly, R. Julliard, S. Kéfi, G. J. Kergoat, S. Lavorel, L. Le
Gall, L. Meslin, S. Morand, X. Morin, H. Morlon, G. Pinay, R. Pradel, F.
M. Schurr, W. Thuiller, and M. Loreau. 2015. Predictive ecology in a
changing world.

\hypertarget{ref-Perretti2013a}{}
Perretti, C. T., S. B. Munch, and G. Sugihara. 2013. Model-free
forecasting outperforms the correct mechanistic model for simulated and
experimental data. Proceedings of the National Academy of Sciences of
the United States of America 110:5253--5257.

\hypertarget{ref-Petchey2015}{}
Petchey, O. L., M. Pontarp, T. M. Massie, S. Kéfi, A. Ozgul, M.
Weilenmann, G. M. Palamara, F. Altermatt, B. Matthews, J. M. Levine, D.
Z. Childs, B. J. McGill, M. E. Schaepman, B. Schmid, P. Spaak, A. P.
Beckerman, F. Pennekamp, and I. S. Pearse. 2015. The ecological forecast
horizon, and examples of its uses and determinants. Ecology Letters
18:597--611.

\hypertarget{ref-VandePol2011}{}
Pol, M. van de, and A. Cockburn. 2011. Identifying the critical climatic
time window that affects trait expression. The American naturalist
177:698--707.

\hypertarget{ref-Queenborough2011}{}
Queenborough, S. A., K. M. Burnet, W. J. Sutherland, A. R. Watkinson,
and R. P. Freckleton. 2011. From meso- to macroscale population
dynamics: A new density-structured approach. Methods in Ecology and
Evolution 2:289--302.

\hypertarget{ref-R2013}{}
R Core Team. 2013. R: A language and environment for statistical
computing.

\hypertarget{ref-Rees2009}{}
Rees, M., and S. P. Ellner. 2009. Integral projection models for
populations in temporally varying environments. Ecological Monographs
79:575--594.

\hypertarget{ref-Schindler2015b}{}
Schindler, D. E., and R. Hilborn. 2015. Prediction, precaution, and
policy under global change. Science 347:953--954.

\hypertarget{ref-Sims2007}{}
Sims, M., D. A. Elston, A. Larkham, D. H. Nussey, and S. D. Albon. 2007.
Identifying when weather influences life-history traits of grazing
herbivores. Journal of Animal Ecology 76:761--770.

\hypertarget{ref-stan2014}{}
Stan Development Team. 2014a. Stan: A C++ Library for Probability and
Sampling, Version 2.5.0.

\hypertarget{ref-rstan2014}{}
Stan Development Team. 2014b. Rstan: the R interface to Stan, Version
2.5.0.

\hypertarget{ref-Suxe6ther2007}{}
Sæther, B. E., S. Engen, V. Grøtan, W. Fiedler, E. Matthysen, M. E.
Visser, J. Wright, A. P. Møller, F. Adriaensen, H. Van Balen, D. Balmer,
M. C. Mainwaring, R. H. McCleery, M. Pampus, and W. Winkel. 2007. The
extended Moran effect and large-scale synchronous fluctuations in the
size of great tit and blue tit populations. Journal of Animal Ecology
76:315--325.

\hypertarget{ref-Taylor2004}{}
Taylor, C. M., and A. Hastings. 2004. Finding optimal control strategies
for invasive species: a density-structured model for Spartina
alterniflora. Journal of Applied Ecology 41:1049--1057.

\hypertarget{ref-Teller2016}{}
Teller, B. J., P. B. Adler, C. B. Edwards, G. Hooker, R. E. Snyder, and
S. P. Ellner. 2016. Linking demography with drivers: climate and
competition. Methods in Ecology and Evolution 7:171--183.

\hypertarget{ref-Vehtari2016}{}
Vehtari, A., A. Gelman, and J. Gabry. 2016. Efficient implementation of
leave-one-out cross-validation and WAIC for evaluating fitted Bayesian
models. ArXiv preprint.

\hypertarget{ref-Wilcox2009}{}
Wilcox, R. R. 2009. Comparing Pearson Correlations: Dealing with
Heteroscedasticity and Nonnormality. Communications in Statistics -
Simulation and Computation 38:2220--2234.

\hypertarget{ref-Ye2015a}{}
Ye, H., R. J. Beamish, S. M. Glaser, S. C. H. Grant, C.-h. Hsieh, L. J.
Richards, J. T. Schnute, and G. Sugihara. 2015. Equation-free
mechanistic ecosystem forecasting using empirical dynamic modeling.
Proceedings of the National Academy of Sciences 112:E1569--E1576.
